---
title: "Alcohol vs Seat choice"
author: "Hayden Wood"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Methods

$H_0$ There is no correlation between seat choice and alchohol consumption

$H_0$ There is a direct correlation between seat choice and alchohol consumption

Catagorical - Seats
Numerical ~ Alchohol consumption

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

This command is to select the data for the ggplot
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  This ggplot is showing x "seats and Y "alchohol". It shows very little in the front with 2 outlines, It shows very little again in the middle with 6 outlines, and finally the back shows a major increase in alchohol consumption with 2 outliers
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This PPplot we just added is very similar to the one we added before but has some visual differences. For example the mean of each seating position is indented. And the outliers for each seat is highlighted in red compared to the black that it laid in
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
This shows 3 seating positions median amount of alcohol consumtion. 0 being the front, 1 being the middle, and 4 being the back.
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
We found that the P value is 0.000116 so we reject $H_0$             
          
## Conclusions

The original problem we had to solve was if Seat, as in seat position in class. And alcohol, as in alchohol consumption has a direct correlation. We found that the median for Front was 0. Median for Middle was 1, and median for Back was 4. This gives us a P value of 0.000116 so we reject $H_0$ because p<0.05